---
title: "MinorGland-QC"
author: "Wenqing Chen"
date: "2022-11-06"
output:
  html_document:
    toc: yes
    toc_depth: 3
    toc_float: yes
    code_folding: hide
    df_print: paged

params:
  workingDir: ~/spidersilk_project/1_single.cell
  MinorResultDir: results/MinorGland
  
---

# library

```{r setup1, include=FALSE}

# install.packages('Seurat') 
# install.packages("tidyverse")

library(Seurat)
library(tidyverse)
library(cowplot)
library(ggplot2)
library(pheatmap)
library(rafalib)
library(ggraph)
library(clustree)

# install.packages('BiocManager')
# BiocManager::install('multtest')
# install.packages('metap')
# BiocManager::install('limma')
# install.packages('harmony')
# install.packages('venn')
# install.packages('pheatmap')
# if(!require(clustree)){install.packages('clustree', dependencies=FALSE)}
```



# add data to the analysis

```{r adding data to the analysis, include=FALSE}

# Load 10x data
Minor01	<-	Read10X(data.dir=	paste(params$workingDir,"data/scRNA/minorGland/P23951_1004/", sep = "/"))
Minor02	<-	Read10X(data.dir=	paste(params$workingDir,"data/scRNA/minorGland/P23951_1008/", sep = "/"))
Minor03	<-	Read10X(data.dir=	paste(params$workingDir,"data/scRNA/minorGland/P23951_1010/", sep = "/"))
Minor04	<-	Read10X(data.dir=	paste(params$workingDir,"data/scRNA/minorGland/P23951_1012/", sep = "/"))
Minor05	<-	Read10X(data.dir=	paste(params$workingDir,"data/scRNA/minorGland/P23951_1014/", sep = "/"))

# Create seurat object
### For Minor01.data, there is a warning: Feature names cannot have underscores ('_'), replacing with dashes ('-')Error in data.frame(row.names = rownames(x = data)) : duplicate row.names: tret1-2, lap-2, thus modified dataset: tret1_2 --> tret1_2.0; lap_2 --> lap_2.0
Minor01.data	<-	CreateSeuratObject(	Minor01 ,	project	=	"Minor_01")
Minor02.data	<-	CreateSeuratObject(	Minor02 ,	project	=	"Minor_02")
Minor03.data	<-	CreateSeuratObject(	Minor03 ,	project	=	"Minor_03")
Minor04.data	<-	CreateSeuratObject(	Minor04 ,	project	=	"Minor_04")
Minor05.data	<-	CreateSeuratObject(	Minor05 ,	project	=	"Minor_05")


# Merging all samples
LarSco.combined <- merge(Minor01.data, y = c(Minor02.data, Minor03.data, Minor04.data, Minor05.data), 
                         add.cell.ids = c("Minor_01", "Minor_02", "Minor_03", "Minor_04", "Minor_05"))

# save
LarSco_dataframe <- data.frame(table(Idents(LarSco.combined)))
sample_cellcount_file <- paste(params$workingDir, params$MinorResultDir, "Sample_cellcount.txt", sep = '/')
write.table(LarSco_dataframe, file = sample_cellcount_file, sep="\t")


```


```{r}

# add more information

LarSco.combined@meta.data
LarSco.combined@assays$RNA@counts

# Add batch Year
Year <- rep("2021",ncol(LarSco.combined))
LarSco.combined <- AddMetaData(LarSco.combined, Year, col.name = "Year")

# Add silking information to metadat
Silk_status <- rep("NotSilked",ncol(LarSco.combined))
LarSco.combined <- AddMetaData(LarSco.combined, Silk_status, col.name = "Silk_status")

# Add batch details to meta data
Batch <- rep("B1",ncol(LarSco.combined))
LarSco.combined <- AddMetaData(LarSco.combined, Batch, col.name = "Batch")


LarSco.combined@meta.data
##
```



# Quality control --- Filter the data 

```{r}


##calculate number of gene per UMI / cell and add to metadata
LarSco.combined$log10GenesPerUmi <- log10(LarSco.combined$nFeature_RNA) / log10(LarSco.combined$nCount_RNA)


## Computing percentage and ratio for MT genes
LarSco.combined$percentMT <- PercentageFeatureSet(LarSco.combined, pattern = '^MT-')
LarSco.combined$RatioMT <- LarSco.combined@meta.data$percentMT / 100

head(LarSco.combined[[]])

# Visualize QC metrics as a violin plot
VlnPlot(LarSco.combined, features = c("nFeature_RNA", "nCount_RNA", "percentMT"), ncol = 3)

# visualize nCountRNA-percentMT relationships
plot1 <- FeatureScatter(LarSco.combined, feature1 = "nFeature_RNA", feature2 = "percentMT")
plot2 <- FeatureScatter(LarSco.combined, feature1 = "nCount_RNA", feature2 = "nFeature_RNA")
plot1 + plot2

```


## filter out low quality cells

```{r}

# filter
LarSco.combined_filtered <- subset(x=LarSco.combined, 
                                   subset = (nCount_RNA >= 400) & (nCount_RNA < 15000) 
                                   & (nFeature_RNA >= 300) & (nFeature_RNA < 2000)  & (percentMT < 5)  )

LarSco.combined_filtered@meta.data


# save

LarSco_Filtered_dataframe <- data.frame(table(Idents(LarSco.combined_filtered)))
sample_cellcount_afetrfilter_file <- paste(params$workingDir, params$MinorResultDir, "Samples_cellcount_afterfiltering.txt", sep = '/')
write.table(LarSco_Filtered_dataframe,
            file = sample_cellcount_afetrfilter_file, sep="\t")

```


## filter lowly expressed genes across the data set

```{r}


# First get the expression matrix
RNAcountsMatrix <- GetAssayData(object = LarSco.combined_filtered, slot = "counts")

# Filtering cells based on genes > 0
NonZero_RNAcountsMatrix <- RNAcountsMatrix > 0

# Calculate row sums
cell_genes =  Matrix::rowSums(NonZero_RNAcountsMatrix)

# keeping genes that are expressed in more than 10 number of cells
keep_genes <- Matrix::rowSums(NonZero_RNAcountsMatrix) >= 10

# Extracting counts
keep_genes_dataframe <- data.frame(keep_genes)

#write.table(keep_genes_dataframe,file = '~/spidersilk_project/MinorGland/minor_QC_results/Intergrated/filtering_genes_Greater10.txt', sep='\t')


keep_genes[grepl(pattern = "MT-", x =names(keep_genes) )] = FALSE 

filtered_RNAcountsMatrix <- RNAcountsMatrix[keep_genes, ]

# Reassigning to filtered seurat object
LarSco.combined_filtered <- CreateSeuratObject(filtered_RNAcountsMatrix, meta.data = LarSco.combined_filtered@meta.data)

LarSco.combined_filtered@meta.data

VlnPlot(LarSco.combined_filtered, features = c("nFeature_RNA", "nCount_RNA", "percentMT"), group.by = "orig.ident", ncol = 3)


# saving filetered seurat object
saveRDS(LarSco.combined_filtered, file = paste(params$workingDir, params$MinorResultDir, "LarSco.combined_filtered.rds", sep = '/'))


```


## calculate how many cells and genes do we have after filtering

```{r print_dims_after_filter}

nCells <- dim(LarSco.combined)[2]
nGenes <- dim(LarSco.combined)[1]
sprintf("Number of cells before filtering: %s", nCells)
sprintf("Number of genes before filtering: %s", nGenes)

nCells_filtered <- dim(LarSco.combined_filtered)[2]
nGenes_filtered <- dim(LarSco.combined_filtered)[1]
sprintf("Number of cells after filtering: %s", nCells_filtered)
sprintf("Number of genes after filtering: %s", nGenes_filtered)


sprintf("Number of cells that are filtered: %s", nCells - nCells_filtered)
sprintf("Number of genes that are filtered: %s", nGenes - nGenes_filtered)

```



# Normalization

```{r}

LarSco.combined_QCfiltered = LarSco.combined_filtered

# “LogNormalize”: normalizes the feature expression measurements for each cell by the total expression, multiplies this by a scale factor (10,000 by default), and log-transforms the result
LarSco.combined_QCfiltered <- NormalizeData(LarSco.combined_QCfiltered, normalization.method = "LogNormalize", scale.factor = 10000)

# Normalized values are stored in LarSco.combined_QCfiltered[["RNA"]]@data
# Visualization
normalized.data <- LarSco.combined_QCfiltered[["RNA"]]@data
normalized.data[1:2, 1:4]
dim(normalized.data)

```



# Identification of highly variable features (feature selection)

```{r}
# highly variable features: highly expressed in some cells, and lowly expressed in others
# Directly modeling the mean-variance relationship inherent in single-cell data
# By default, we return 2,000 features per dataset. These will be used in downstream analysis, like PCA


LarSco.combined_QCfiltered <- FindVariableFeatures(LarSco.combined_QCfiltered, selection.method = "vst", nfeatures = 2000)

# # Identify the 10 most highly variable genes
top10 <- head(VariableFeatures(LarSco.combined_QCfiltered), 10)
#top10

# plot variable features with and without label
plot1 <- VariableFeaturePlot(LarSco.combined_QCfiltered)
plot2 <- LabelPoints(plot = plot1, points = top10, repel = TRUE)
plot1 + plot2

``` 



# Scaling the data

```{r}
# After scaling, for each gene, the mean expression across cells is 0 and the variance across cells is 1
# This step gives equal weight in downstream analyses, so that highly-expressed genes do not dominate


# scaling all genes
all.genes <- rownames(LarSco.combined_QCfiltered)
LarSco.combined_QCfiltered <- ScaleData(LarSco.combined_QCfiltered, features = all.genes)

top50 <- head(VariableFeatures(LarSco.combined_QCfiltered), 50)

```



# Perform linear dimensional reduction

```{r}

# Principal Component Analysis (PCA)
# set.seed() is used to seed random numbers, a specific seed can produce a specific pseudo-random sequence, the main purpose of this function is to make your simulation repeatable
LarSco.combined_QCfiltered <- RunPCA(LarSco.combined_QCfiltered, features = VariableFeatures(object = LarSco.combined_QCfiltered), seed.use = 1234)

# Visualization

# VizDimLoadings(LarSco.combined_QCfiltered, dims = 1:2, reduction = "pca")

DimPlot(LarSco.combined_QCfiltered, reduction = "pca", group.by = "orig.ident")+NoAxes()+ggtitle("PCA raw_data")
ggsave(paste(params$workingDir, params$MinorResultDir, "PCA raw_data.pdf", sep = '/'), width = 10, height = 10)


DimPlot(LarSco.combined_QCfiltered, group.by = "Batch", reduction = "pca", pt.size = 1.5)
DimHeatmap(LarSco.combined_QCfiltered, dims = 1, cells = 500, balanced = TRUE)
DimHeatmap(LarSco.combined_QCfiltered, dims = 1:20, cells = 500, balanced = TRUE)

```



# Determine the ‘dimensionality’ of the dataset

```{r}

LarSco.combined_QCfiltered <- JackStraw(LarSco.combined_QCfiltered, num.replicate = 100)
LarSco.combined_QCfiltered <- ScoreJackStraw(LarSco.combined_QCfiltered, dims = 1:20)


JackStrawPlot(LarSco.combined_QCfiltered, dims = 1:20)
ggsave(paste(params$workingDir, params$MinorResultDir, "JackStrawPlot.pdf", sep = '/'), width = 10, height = 10)

ElbowPlot(LarSco.combined_QCfiltered)
ggsave(paste(params$workingDir, params$MinorResultDir, "ElbowPlot.pdf", sep = '/'), width = 10, height = 10)

```



# Cluster the cells

```{r}

# first construct a KNN graph based on the euclidean distance in PCA space, and refine the edge weights between any two cells based on the shared overlap in their local neighborhoods
LarSco.combined_QCfiltered <- FindNeighbors(LarSco.combined_QCfiltered, dims = 1:20)

# Group cells together

# Resolution parameter: sets the ‘granularity’ of the downstream clustering, with increased values leading to a greater number of clusters
# Setting this parameter between 0.4-1.2 typically returns good results for single-cell datasets of around 3K cells
LarSco.combined_QCfiltered <- FindClusters(LarSco.combined_QCfiltered, resolution = 0.4)


# The clusters can be found using the Idents() function.
# Look at cluster IDs of the first 5 cells
head(Idents(LarSco.combined_QCfiltered), 5)

```



# Run non-linear dimensional reduction (UMAP)

```{r}

# UMAP
# reticulate::py_install(packages = 'umap-learn')
LarSco.combined_QCfiltered <- RunUMAP(LarSco.combined_QCfiltered, dims = 1:20, seed.use = 1234)
LarSco.combined_QCfiltered <- RunTSNE(LarSco.combined_QCfiltered, dims = 1:20)

# Visualization
DimPlot(LarSco.combined_QCfiltered, reduction = "umap", group.by = "seurat_clusters" , label = TRUE, label.size = 5)
ggsave(paste(params$workingDir, params$MinorResultDir, "umap_1.pdf", sep = '/'), width = 10, height = 10)

DimPlot(LarSco.combined_QCfiltered, reduction = "umap", group.by = "orig.ident" , label = TRUE, label.size = 5)
ggsave(paste(params$workingDir, params$MinorResultDir, "umap_2.pdf", sep = '/'), width = 10, height = 10)

DimPlot(LarSco.combined_QCfiltered, reduction = "umap", group.by = "Batch" , label = TRUE, label.size = 5)


```


```{r}
# saving QC filetered seurat object
saveRDS(LarSco.combined_QCfiltered, file = paste(params$workingDir, params$MinorResultDir, "LarSco.combined_QCfiltered.rds", sep = '/'))


```

######################################################

# Integrate

## Read filtered RDS file

```{r}

LarSco.combined_filtered <- readRDS(file = paste(params$workingDir, params$MinorResultDir, "LarSco.combined_filtered.rds", sep = '/'))

```

## FindIntegrationAnchors

```{r}

# Integration through FindIntegrationAnchors

LarSco.combined_filtered.list <- SplitObject(LarSco.combined_filtered, split.by = "orig.ident")

# normalize and identify variable features for each dataset independently
LarSco.combined_filtered.list <- lapply(X = LarSco.combined_filtered.list, FUN = function(x) {
    x <- NormalizeData(x)
    x <- FindVariableFeatures(x, selection.method = "vst", nfeatures = 2000)
})

# select features that are repeatedly variable across datasets for integration run PCA on each dataset using these features
features <- SelectIntegrationFeatures(object.list = LarSco.combined_filtered.list)
write.table(features, file = paste(params$workingDir, params$MinorResultDir, "integration/Integrate_features.txt", sep = "/"))

# add important marker genes to the features
Minor_All_Markers <- read_tsv(paste(params$workingDir, params$MinorResultDir, "integration/allmarkers_join_geneinfo.tsv", sep = "/"))
top5.Minor_All_Markers <- Minor_All_Markers %>%
    group_by(cluster) %>%
    slice_max(n = 5, order_by = avg_log2FC)
top5.Minor_All_Markers_Gene <- top5.Minor_All_Markers$gene
New_features <- unique(c(features, top5.Minor_All_Markers_Gene))
write.table(New_features, 
            file = paste(params$workingDir, params$MinorResultDir, "integration_add_MarkerGenes/Integrate_features_add_Markers.txt", sep = "/"))

LarSco.combined_filtered.list <- lapply(X = LarSco.combined_filtered.list, FUN = function(x) {
    x <- ScaleData(x, features = New_features, verbose = FALSE)
    x <- RunPCA(x, features = New_features, verbose = FALSE)
})

# create an 'integrated' data assay
LarSco.combined_filtered.anchors <- FindIntegrationAnchors(object.list = LarSco.combined_filtered.list, anchor.features = New_features,
                                                           reduction = "rpca", k.anchor = 70)
saveRDS(LarSco.combined_filtered.anchors, paste(params$workingDir, params$MinorResultDir, "integration_add_MarkerGenes/Minor_integration.anchors.rds", sep = "/"))


LarSco.combined_filtered.int <- IntegrateData(anchorset = LarSco.combined_filtered.anchors)
saveRDS(LarSco.combined_filtered.int, paste(params$workingDir, params$MinorResultDir, "integration_add_MarkerGenes/LarSco.combined_filtered.int.rds", sep = "/"))

```



```{r}
LarSco.combined_filtered.int <- readRDS(paste(params$workingDir, params$MinorResultDir, "integration_add_MarkerGenes/LarSco.combined_filtered.int.rds", sep = '/'))
DefaultAssay(LarSco.combined_filtered.int) <- "integrated"

# Run the standard workflow for visualization and clustering
LarSco.combined_filtered.int <- ScaleData(LarSco.combined_filtered.int, verbose = FALSE)
LarSco.combined_filtered.int <- RunPCA(LarSco.combined_filtered.int, npcs = 20, verbose = FALSE)
LarSco.combined_filtered.int <- RunUMAP(LarSco.combined_filtered.int, reduction = "pca", dims = 1:20)
LarSco.combined_filtered.int <- RunTSNE(LarSco.combined_filtered.int, dims = 1:20)

LarSco.combined_filtered.int <- FindNeighbors(LarSco.combined_filtered.int, reduction = "pca", dims = 1:20)
LarSco.combined_filtered.int <- FindClusters(LarSco.combined_filtered.int, resolution = 0.4)

# Visualization
p1 <- DimPlot(LarSco.combined_filtered.int, reduction = "umap", group.by = "orig.ident")
p2 <- DimPlot(LarSco.combined_filtered.int, reduction = "umap", label = TRUE, repel = TRUE)    
p1 + p2

```

```{r}
# Visualization
DimPlot(LarSco.combined_filtered.int, reduction = "umap", group.by = "seurat_clusters" , label = TRUE, label.size = 5)
ggsave(paste(params$workingDir, params$MinorResultDir, "integration_add_MarkerGenes","sample_int_umap_1.pdf", sep = '/'), width = 10, height = 10)

DimPlot(LarSco.combined_filtered.int, reduction = "umap", group.by = "orig.ident" , label = TRUE, label.size = 5)
ggsave(paste(params$workingDir, params$MinorResultDir,"integration_add_MarkerGenes", "sample_int_umap_2.pdf", sep = '/'), width = 10, height = 10)

DimPlot(LarSco.combined_filtered.int, reduction = "umap", group.by = "Batch" , label = TRUE, label.size = 5)
ggsave(paste(params$workingDir, params$MinorResultDir, "integration_add_MarkerGenes","sample_int_umap_3.pdf", sep = '/'), width = 10, height = 10)

```


```{r}

# Save
integrated_RDSfile <- paste(params$workingDir, params$MinorResultDir,"integration_add_MarkerGenes", "LarSco.combined_filtered.int.rds", sep = '/')
saveRDS(LarSco.combined_filtered.int, file = integrated_RDSfile)

```


# Check the resolution
```{r}
LarSco.combined_filtered.int@meta.data
names(LarSco.combined_filtered.int@graphs)

for (res in c( 0.3, 0.4 , 0.5 , 0.6 )){
  LarSco.combined_filtered.int <- FindClusters(LarSco.combined_filtered.int, graph.name = "integrated_snn", resolution = res, algorithm = 1)
}

LarSco.combined_filtered.int <- readRDS(paste(params$workingDir, params$MinorResultDir,"integration_add_MarkerGenes", "LarSco.combined_filtered.int.rds", sep = '/'))
plot_grid(ncol = 4,
  DimPlot(LarSco.combined_filtered.int, reduction = "umap", group.by = "integrated_snn_res.0.3")+ggtitle("louvain_0.3"),
  DimPlot(LarSco.combined_filtered.int, reduction = "umap", group.by = "integrated_snn_res.0.4")+ggtitle("louvain_0.4"),
  DimPlot(LarSco.combined_filtered.int, reduction = "umap", group.by = "integrated_snn_res.0.5")+ggtitle("louvain_0.5"),
  DimPlot(LarSco.combined_filtered.int, reduction = "umap", group.by = "integrated_snn_res.0.6")+ggtitle("louvain_0.6")
  )

clustree(LarSco.combined_filtered.int@meta.data, prefix = "integrated_snn_res.")
ggsave(paste(params$workingDir, params$MinorResultDir,"integration_add_MarkerGenes", "Clustree.pdf", sep = '/'), width = 10, height = 10)
# choose resolution = 0.4
LarSco.combined_filtered.int <- FindClusters(LarSco.combined_filtered.int, graph.name = "integrated_snn", resolution = 0.4, algorithm = 1)
# Save
saveRDS(LarSco.combined_filtered.int, file = paste(params$workingDir, params$MinorResultDir,"integration_add_MarkerGenes", "LarSco.combined_filtered.int.rds", sep = '/'))

```


# visualisation of the different clusters
```{r}

LarSco.combined_filtered.int@meta.data
DefaultAssay(LarSco.combined_filtered.int) <- "integrated"

LarSco.combined_filtered.int <- FindClusters(LarSco.combined_filtered.int, resolution = 0.4)
umap = DimPlot(LarSco.combined_filtered.int, reduction = "umap", group.by = "seurat_clusters", label = TRUE )
F_minor <- FeaturePlot( LarSco.combined_filtered.int, features = c('MiSpa', 'MiSpb','MiSpc', 'MiSpd','spa', 'Spidroin3', 'LASC013229', 'xync', 'obst-e-2',  'obst-e-5'))
F_minor_1 <- FeaturePlot( LarSco.combined_filtered.int, features = c('MiSpa', 'MiSpb','MiSpc', 'MiSpd'), split.by = "orig.ident")

# visualisation based on Batch

GB1_batch = LarSco.combined_filtered.int@meta.data %>%
  ggplot(aes(seurat_clusters, fill = Batch)) +
  geom_bar()+ 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
GB2_batch = LarSco.combined_filtered.int@meta.data %>% 
  ggplot(aes(seurat_clusters, fill = Batch)) +
  geom_bar( position = "fill")+ 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))


LarSco.combined_filtered.int@meta.data$expression = "low"
LarSco.combined_filtered.int@meta.data$expression[LarSco.combined_filtered.int@meta.data$nCount_RNA > 1000] = "medium"
LarSco.combined_filtered.int@meta.data$expression[LarSco.combined_filtered.int@meta.data$nCount_RNA > 4000] = "high"

GB1_batch_expression = LarSco.combined_filtered.int@meta.data %>% ggplot(aes(seurat_clusters, fill = expression)) + geom_bar()+ theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
GB2_batch_expression = LarSco.combined_filtered.int@meta.data %>% ggplot(aes(seurat_clusters, fill = expression)) + geom_bar( position = "fill")+ theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

D1 = DimPlot(LarSco.combined_filtered.int, group.by="seurat_clusters",  split.by =  c("Batch"), ncol=3, label = TRUE ) +NoAxes() + theme(legend.position = "none")


# show figure
umap_without_legend = umap + theme(legend.position = "none")
(umap_without_legend + D1) / (GB1_batch + GB1_batch_expression) / (GB2_batch + GB2_batch_expression)

# save figure
ggsave("../../data/scRNA/minorGland/cells_distribution_among_clusters_batch.pdf", width = 20, height = 20)


```



```{r}
LarSco.combined_filtered.int <- readRDS(file = paste(params$workingDir, params$MinorResultDir,"integration_add_MarkerGenes", "LarSco.combined_filtered.int.rds", sep = '/'))

source("colorSchemes.R")
AmpullateColors_2 <- AmpullateColors_2()


# visualisation based on samples
GB1_ident = LarSco.combined_filtered.int@meta.data %>%
  ggplot(aes(seurat_clusters, fill = orig.ident)) +
  geom_bar()+ 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

GB2_ident = LarSco.combined_filtered.int@meta.data %>% 
  ggplot(aes(seurat_clusters, fill = orig.ident)) +
  geom_bar( position = "fill")+ 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))


GB1 = LarSco.combined_filtered.int@meta.data %>% ggplot(aes(Batch, fill = orig.ident)) + geom_bar()+ theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

# show figure
(GB1_ident + GB2_ident) / (GB1 + umap)
GB1_ident + umap
# save figure
ggsave(paste(params$workingDir, params$MinorResultDir,"integration_add_MarkerGenes", "cells_distribution_among_clusters_samples.pdf", sep = '/'), GB1_ident + umap, width = 10, height = 5)

# add colors
GB1_ident_cols = LarSco.combined_filtered.int@meta.data %>%
  ggplot(aes(seurat_clusters, fill = orig.ident)) +
  geom_bar(identity = "fill") + 
  scale_fill_manual(values = AmpullateColors_2) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

Dim_1 <- DimPlot(LarSco.combined_filtered.int, reduction = "umap", group.by = "orig.ident" , label = TRUE, label.size = 5, cols = AmpullateColors_2)

ggsave(paste(params$workingDir, params$MinorResultDir,"integration_add_MarkerGenes", "GB1_ident_cols.pdf", sep = '/'), GB1_ident_cols)
ggsave(paste(params$workingDir, params$MinorResultDir,"integration_add_MarkerGenes", "Dim_1.pdf", sep = '/'), Dim_1)

```

